---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit README.Rmd -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# R Package binomial  

This is a workout assignment from STAT 133.  

***

The purpose of this assignment is to create an R package that implements functions for calculating probabilities of a binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.  

***  

#### **Author**  
Yi-Chen Chen
  
  

***  
  
  

## Overview

`"binomial"` is an [R](http://www.r-project.org/) package that provides functions for calculating probabilities of a binomial random variable, and related calcualtions such as the probability distribution, the expected value, variance, etc.


## Motivation 

This package has been developed to help the author get in touched with building R packages and provide tools for calculating probabilties of binomial random variables.


## Installation

Install the development version from GitHub via the package `"devtools"`:

``` r
# development version from GitHub:
install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-mingyueyang/binomial")
# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-mingyueyang/binomial", build_vignettes = TRUE)
```

## Usage

```{r example}
library(binomial)
## some examples
# binomial probability of getting 2 successes in 5 trials,assuming prob of success = 0.5
bin_probability(success = 2, trials = 5, prob = 0.5)
# binomial probability distribution of getting possible successes in 5 trials,assuming prob of success = 0.5
bin_distribution(trials = 5, prob = 0.5)
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
# binomial cumulative distribution  of getting possible successes in 5 trials,assuming prob of success = 0.5
bin_cumulative(trials = 5, prob = 0.5)
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
# binomial variable
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
# summary of a binomial variable
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
# functions of measures
bin_mean(10,0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```