---
title: "Introduction to Package binomial"
author: "Yi-Chen Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```


## Binomial

The package `binomial` allows the user to experiment with different calculations and visualizations of a binomial random variable.

## Creating a `bin_var`

The first step is to create a *bin_var* object with the function `bin_variable()` which takes in two arguments: *trials* and *prob*:

```{r}
bin_var <- bin_variable(trials = 5, prob = 0.5)
bin_var
```


## Summary statistics

Now that we have a *bin_var* object, we can view the different summary statistics of *bin_var* by using the function `summary()`.

```{r}
summary(bin_var)
```

We can also view only the specific statistic of *bin_var* (e.g. mean, variance, mode, skewness, and kurtosis) by functions listed below (`bin_mean(trials, prob)`, `bin_variance(trials, prob)`, `bin_mode(trials, prob)`, `bin_skewness(trials, prob)`, `bin_kurtosis(trials, prob)`)

```{r}
bin_mean(trials = 5, prob = 0.5)
bin_variance(trials = 5, prob = 0.5)
bin_mode(trials = 5, prob = 0.5)
bin_skewness(trials = 5, prob = 0.5)
bin_kurtosis(trials = 5, prob = 0.5)
```

## Probability

To calculate the binomial probability at a specific number of success, you can use the `bin_probability()` function.

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

The `bin_choose()` function calculates "n choose k"

```{r}
bin_choose(n = 5, k = 2)
```


## Tables and Plots

You can use the function `bin_distribution()` to create tables of the binomial probability distribution and the cumulative binomial distribution respectively.

```{r}
bin_dis <- bin_distribution(trials = 5, prob = 0.5)
bin_dis
```

To visualize the probability distribution, use the `plot()` function.

```{r}
plot(bin_dis)
```

You can also use the function `bin_cumulative()` to create a table of the cumulative binomial probability distribution.

```{r}
bin_cum <- bin_cumulative(trials = 5, prob = 0.5)
bin_cum
```

Similarly, you can visualize the probability distribution using the `plot()` function.

```{r}
plot(bin_cum)
```